### 2020-04-24 manuscript.rmd
github URL update.

#### Availability of Data  
Data, model code, and code used to produce the figures is available at github.com/bjkellyio.

>>>>

#### Availability of Data  
Data, model code, and code used to produce the figures is available at https://github.com/bjklab/Sputum-quantity-and-adverse-events-during-mechanical-ventilation.
